|

### 2023-03-06 paper_comparison/paper_comparison/paper_comparison.Rmd
update the effect size desc

(do we actually need the penalty term?)

Effect size $E$ can be defined as the difference of a parameter for a particular model or distribution, or a statistic derived from a sample. Importantly, it needs to reflect the treatment we try to measure. According to the underlying simulated model, we define the effect size $E = \sqrt{n}/(\sigma k)$ for the non-linearity model and $E = b\sqrt{n}/(|a| + 1)$ for the heteroskedasticity model. The parameter $k$ is the number of turning points embedded in the residual plot. It is used as a penalty term to reduce the effect size for complex shapes. There are one, two, three and five turning points in "U", "S", "M", "Triple-U" shape respectively.  The denominator of the effect size of the heteroskedasticity model is $|a| + 1$. It is used to

>>>>

Effect size $E$ can be defined as the difference of a parameter for a particular model or distribution, or a statistic derived from a sample. Importantly, it needs to reflect the treatment we try to measure. According to the underlying simulated model, we define the effect size

$$E = \frac{1}{2}\left(\boldsymbol{\mu}_z'[diag(\boldsymbol{R}_a\sigma^2)]^{-1}\boldsymbol{\mu}_z\right)$$

for the non-linearity model, and

$$E = \frac{1}{2}\left(log\frac{|diag(\boldsymbol{R}_a\boldsymbol{V}\boldsymbol{R}_a')|}{|diag(\boldsymbol{R}_a)|} - n + tr(diag(\boldsymbol{R}_a\boldsymbol{V}\boldsymbol{R}_a')^{-1}diag(\boldsymbol{R}_a))\right)$$
for the heteroskedasticity model, where $diag(.)$ is the diagonal matrix constructed from the diagonal elements of a matrix, $\sigma^2\boldsymbol{I}$ is the assumed covariance matrix of the error term when $H_0$ is true, $\boldsymbol{V}$ is the actual covariance matrix of the error term, $\boldsymbol{R}_a = \boldsymbol{I}_n - \boldsymbol{H}_a$ is the residual operator, $\boldsymbol{H}_a = \boldsymbol{X}_a(\boldsymbol{X}_a'\boldsymbol{X}_a)^{-1}\boldsymbol{X}_a'$ is the hat matrix, $\boldsymbol{X}_a = (\boldsymbol{1},  \boldsymbol{X})$ is the matrix of predictors including the intercept used in the regression equation, and $\boldsymbol{\mu}_z = \boldsymbol{R}_a\boldsymbol{Z}\boldsymbol{\beta}_z$ is the expected values of residuals with $\boldsymbol{Z}$ be any higher order terms of $\boldsymbol{X}$ leave out by the regression equation and $\boldsymbol{\beta}_z$ be the corresponding coefficients.

Both equations above are derived from the Kullback-Leibler divergence (citation here?) and the details are provided in the appendix.
